---
title: "Project Assignment 1"
author: "Veronica Vaca"
date: "14 de junio de 2017"
output: html_document
---

# Reproducible Research: Peer Assessment 1

This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals throughout the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

This document presents the results from Project Assignment 1 in the Coursera course Reproducible Research, written in a single R markdown document that can be processed by knitr and transformed into an HTML file.

## Load in the necessary packages
```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

require(knitr)
opts_chunk$set(echo = TRUE)

require(ggplot2); require(lubridate)
require(scales);require(dplyr)
require(Hmisc);
```

## Loading and preprocessing the data
NOTE: It is assumed that you have already downloaded the activity.csv and saved it in your working directory. If not, please download the code here, unzip it and save it to your working directory.

##### 1. Load the data (i.e. read.csv())
```{r, results='markup', warning=TRUE, message=TRUE}
if(!file.exists('activity.csv')){
    unzip('repdata_data_activity.zip')
}
datos <- read.csv('activity.csv')
```
##### 2. Process/transform the data (if necessary) into a format suitable for your analysis

View the data and change formats if it is necessary

```{r}
str(datos)
describe(datos$date)
datos$date <- as.Date(as.character(datos$date),"%Y-%m-%d")
head(datos)

```

-----

## What is mean total number of steps taken per day?

For this part of the assignment the missing values can be ignored.

* Calculate the total number of steps taken per day.
* Make a histogram of the total number of steps taken each day.
* Calculate and report the mean and median of the total number of steps taken per day.

```{r}
stepsBD <- tapply(datos$steps, datos$date, sum, na.rm=TRUE)
head(stepsBD)

```

##### 1. Make a histogram of the total number of steps taken each day
```{r}
qplot(stepsBD, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```

##### 2. Calculate and report the mean and median total number of steps taken per day
```{r}
stepsBDMean <- mean(stepsBD,na.rm=T)
stepsBDMedian <- median(stepsBD,na.rm=T)
```
* Mean: `r stepsBDMean`
* Median:  `r stepsBDMedian`

-----

## What is the average daily activity pattern?

##### 1. Make a time series plot

##### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
----

## Imputing missing values
##### 1. Calculate and report the total number of missing values in the dataset 


##### 2. Devise a strategy for filling in all of the missing values in the dataset.
##### 3. Create a new dataset that is equal to the original dataset but with the missing data filled in.


##### 4. Make a histogram of the total number of steps taken each day 
